\Large\bf Scalable and Probabilistic Leaderless BFT Consensus through Metastability

### 2020-11-05 paper_fr.tex
S2 - Sureté, Vitalité

\begin{abstract}
%O This paper introduces a family of leaderless Byzantine fault tolerance protocols, built around a metastable mechanism via network subsampling.
Cet article présente une famille de protocoles à tolérance de faute byzantine sans dirigeant, bâtis autour d'un mécanisme métastable via sous-échantillonnage réseau.
%O These protocols provide a strong probabilistic safety guarantee in the presence of Byzantine adversaries while their concurrent and leaderless nature enables them to achieve high throughput and scalability.
Ces protocoles fournissent une forte garantie de sûreté probabiliste en présence d'adversaires byzantins, tandis que leur nature simultanée et sans dirigeant leur permet d'être performants et extensibles.
%O Unlike blockchains that rely on proof-of-work, they are quiescent and green.
Contrairement aux blockchains fondées sur la preuve de travail (\emph{proof-of-work}), ils sont économes et écologiques.
%O Unlike traditional consensus protocols where one or more nodes typically process linear bits in the number of total nodes per decision, no node processes more than logarithmic bits. It does not require accurate knowledge of all participants and exposes new possible tradeoffs and improvements in safety and liveness for building consensus protocols.
Contrairement aux protocoles de consensus traditionnels où un ou plusieurs nœuds traitent typiquement des bits de manière linéaire dans les nombres de nœuds totaux par décisiono, aucun nœud ne les traite plus que de manière logarithmique. HOULA
%Finally, unlike traditional consensus protocols and similar to longest-chain protocols, our protocols provide increase in both liveness and safety guarantees when the observed adversarial presence decreases below the maximal expected bound.

@@

%O The paper describes the Snow protocol family, analyzes its guarantees, and describes how it can be used to construct the core of an internet-scale electronic payment system called Avalanche, which is evaluated in a large scale deployment.
Cet article décrit la famille de protocoles Snow, analyse ses garanties et décrit la manière dont il peut être utilisé pour construire le cœur d'un système de paiement électronique à l'échelle de l'internet appelé Avalanche, qui est évalué lors d'un déploiement à grande échelle.
%O Experiments demonstrate that the system can achieve high throughput (3400 tps), provide low confirmation latency (1.35 sec), and scale well compared to existing systems that deliver similar functionality. For our implementation and setup, the bottleneck of the system is in transaction verification.
Les expériences démontrent que le système peut atteindre un haut début (3400 tps), fournir une faible latence de confirmation (1,35 s) et correctement passer à l'échelle par rapport à d'autres systèmes offrant des fonctionnalités similaires. Le goulet d'étranglement du système dans l'implémentation et la configuration retenue est la vérification des transations.
\end{abstract}

@@

L'accord parmi un ensemble d'hôtes distribués se trouve au cœur d'innombrables applications allant de services à l'échelle de l'Internet servant des milliards de gens~\cite{Burrows06,HuntKJR10} à des cryptomonnaies valant des milliards de dollars~\cite{marketcapcryptocurrency}.

@@

Bitcoin consomme actuellement autour de 63.49 TWh/an~\cite{bitcoinpower}, environ deux fois l'énergie pour le Danemark~\cite{denmarkpower}.

@@

\section{Model and Goals}
\label{sec:model_and_goals}
% \editchange{Because our Snowball family provides strong safety guarantee and liveness guarantee},
% it is possible to build other applications involving large-scale probabilistic consensus. We focus on a cryptocurrency application because of many challenges it poses.
%Nevertheless, Snowball does provide liveness guarantee for conflicting values, so it is possible to extend this single-decree protocol for other possible applications involving large-scale probabilistic consensus.
%\Jon{Are there other applications where this consensus model would be valuable? It's not a BFT RSM, but it would be very intriguing if there were other additional applications.}

\tronly{\paragraph{Key Guarantees}}{}

@@

\paragraph{Safety} Unlike classical consensus protocols, and similar to longest-chain-based consensus protocols such as Nakamoto consensus~\cite{nakamoto2008bitcoin}, we adopt an $\varepsilon$-safety guarantee that is probabilistic. 
In practice, this probabilistic guarantee is as strong as traditional safety guarantees, since appropriately small choices of $\varepsilon$ can render consensus failure negligible, lower than the probability of hardware failure due to random events.
Figure~\ref{fig:fandepsilon} shows how the portion ($f/n$) of misbehaving participants (or computation power) affects the probability of system safety failure (decision of two conflicting proposals), given a choice of finality.
% The maximum tolerated Byzantine presence $f$, is dependent on the choice of $\varepsilon$. Similar to Nakamoto consensus, given an observed Byzantine presence $f'$, where $f' \leq f$, the safety failure probability of our protocols maintains the property that $\varepsilon' \leq \varepsilon$. On the other hand, for classical consensus protocols, the failure probability is simply zero for all $f' \leq f$, and almost sure (i.e. one) for $f' > f$.

\begin{figure}[h]
    \includegraphics[width=\linewidth]{figures/safety-f-eps.pdf}
    \caption{Classical BFT protocols that tolerate $f$ failures will encounter total safety failure when the threshold is exceeded even by one additional node. The Bitcoin curve shows a typical finality choice for Bitcoin where a block is considered final when it is ``buried'' in a branch having 6 additional blocks compared to any other competing forks. Snowflake belongs to the Snow family, and it is configured with $k=10$, $\beta=150$. Snowflake-7,8 uses $\alpha=7$ and $\alpha=8$ respectively (see Section~\ref{sec:protocol} for the definition of $k$, $\alpha$ and $\beta$.}
    \label{fig:fandepsilon}
\end{figure}

\tronly{%
\begin{figure}[h]
    \includegraphics[width=\linewidth]{figures/safety-f-eps-log.pdf}
    \caption{Figure~\ref{fig:fandepsilon} with log-scaled y-axis.}
    \label{fig:fandepsilonlog}
\end{figure}
}{}

\paragraph{Liveness} All our protocols provide a non-zero probability guarantee of termination within a bounded amount of time. 
This bounded guarantee is similar to various protocols such as Ben-Or~\cite{ben1983another} and longest-chain protocols.
In particular, for Nakamoto consensus, the number of required blocks for a transaction increases exponentially with the number of adversarial nodes, with an asymptote at $f = n/2$ wherein the number is infinite.
In other words, the time required for finality approaches $\infty$ as $f$ approaches $n/2$\tronly{ (Figure~\ref{fig:livenessproperties}).}{.}
Furthermore, the required number of rounds is calculable ahead of time, as to allow the system designer to tune liveness at the expense of safety. Lastly, unlike traditional consensus protocols and similar to Nakamoto, our protocols benefit from lower adversarial presence, as discussed in property P3 below.

\tronly{%
\begin{figure}[h!]
    \includegraphics[width=\linewidth]{figures/liveness-f-time.pdf}
    \caption{The relation between $f/n$ and the convergence speed, given $\varepsilon = 10^{-20}$. The left figure shows the expected number of blocks to guarantee $\varepsilon$ in Bitcoin, which, counter to commonly accepted folk wisdom, is not a constant $6$, but depends on adversary size to withhold the same $\varepsilon$. The right figure shows the maximum number of rounds required by Snowflake, where being different from Bitcoin, the asymptote is below $0.5$ and varies by the choice of parameters.}
    \label{fig:livenessproperties}
\end{figure}
}

>>>>

\begin{abstract}
%O This paper introduces a family of leaderless Byzantine fault tolerance protocols, built around a metastable mechanism via network subsampling.
Cet article présente une famille de protocoles à tolérance de faute byzantine sans dirigeant, bâtis autour d'un mécanisme métastable via sous-échantillonnage réseau.
%O These protocols provide a strong probabilistic safety guarantee in the presence of Byzantine adversaries while their concurrent and leaderless nature enables them to achieve high throughput and scalability.
Ces protocoles fournissent une forte garantie de sûreté probabiliste en présence d'adversaires byzantins, tandis que leur nature simultanée et sans dirigeant leur permet d'être performants et extensibles.
%O Unlike blockchains that rely on proof-of-work, they are quiescent and green.
Contrairement aux blockchains fondées sur la preuve de travail (\emph{proof-of-work}), ils sont économes et écologiques.
%O Unlike traditional consensus protocols where one or more nodes typically process linear bits in the number of total nodes per decision, no node processes more than logarithmic bits. It does not require accurate knowledge of all participants and exposes new possible tradeoffs and improvements in safety and liveness for building consensus protocols.
Contrairement aux protocoles de consensus traditionnels où un ou plusieurs nœuds traitent typiquement des bits de manière linéaire dans les nombres de nœuds totaux par décision, aucun nœud ne les traite plus que de manière logarithmique. HOULA
%Finally, unlike traditional consensus protocols and similar to longest-chain protocols, our protocols provide increase in both liveness and safety guarantees when the observed adversarial presence decreases below the maximal expected bound.

@@

%O The paper describes the Snow protocol family, analyzes its guarantees, and describes how it can be used to construct the core of an internet-scale electronic payment system called Avalanche, which is evaluated in a large scale deployment.
Cet article décrit la famille de protocoles Snow, analyse ses garanties et décrit la manière dont il peut être utilisé pour construire le cœur d'un système de paiement électronique à l'échelle de l'internet appelé Avalanche, qui est évalué lors d'un déploiement à grande échelle.
%O Experiments demonstrate that the system can achieve high throughput (3400 tps), provide low confirmation latency (1.35 sec), and scale well compared to existing systems that deliver similar functionality. For our implementation and setup, the bottleneck of the system is in transaction verification.
Les expériences démontrent que le système peut atteindre un haut débit (3400~tps), fournir une faible latence de confirmation (1,35~s) et correctement passer à l'échelle par rapport à d'autres systèmes offrant des fonctionnalités similaires. Le goulet d'étranglement du système dans l'implémentation et la configuration retenue est la vérification des transations.
\end{abstract}

@@

L'accord parmi un ensemble d'hôtes distribués se retrouve au cœur d'innombrables applications allant de services à l'échelle de l'Internet servant des milliards de gens~\cite{Burrows06,HuntKJR10} à des cryptomonnaies valant des milliards de dollars~\cite{marketcapcryptocurrency}.

@@

Bitcoin consomme actuellement autour de 63.49 TWh/an~\cite{bitcoinpower}, environ deux fois l'énergie consommée par le Danemark~\cite{denmarkpower}.

@@

%O \section{Model and Goals}
\section{Modèle et buts}
\label{sec:model_and_goals}
% \editchange{Because our Snowball family provides strong safety guarantee and liveness guarantee},
% it is possible to build other applications involving large-scale probabilistic consensus. We focus on a cryptocurrency application because of many challenges it poses.
%Nevertheless, Snowball does provide liveness guarantee for conflicting values, so it is possible to extend this single-decree protocol for other possible applications involving large-scale probabilistic consensus.
%\Jon{Are there other applications where this consensus model would be valuable? It's not a BFT RSM, but it would be very intriguing if there were other additional applications.}

%O \tronly{\paragraph{Key Guarantees}}{}
\tronly{\paragraph{Garanties clefs}}{}

@@

%O \paragraph{Safety} Unlike classical consensus protocols, and similar to longest-chain-based consensus protocols such as Nakamoto consensus~\cite{nakamoto2008bitcoin}, we adopt an $\varepsilon$-safety guarantee that is probabilistic. 
\paragraph{Sûreté} À l'inverse des protocoles de consensus classiques, et de même que les protocoles de consensus fondés sur la chaîne la plus longue~\cite{nakamoto2008bitcoin}, nous adoptions une garantie de sûreté-$\varepsilon$ qui est probabiliste.
%O In practice, this probabilistic guarantee is as strong as traditional safety guarantees, since appropriately small choices of $\varepsilon$ can render consensus failure negligible, lower than the probability of hardware failure due to random events.
En pratique, cette garantie probabiliste est aussi forte que les garantie de sûreté traditionnelles, puisque le choix d'un petit $\varepsilon$ peut rendre la défaillance du consensus négligeable, inférieurs à la probabilité d'une panne matérielle due à des événements imprévisibles.
%OFigure~\ref{fig:fandepsilon} shows how the portion ($f/n$) of misbehaving participants (or computation power) affects the probability of system safety failure (decision of two conflicting proposals), given a choice of finality.
La figure~\ref{fig:fandepsilon} montre comment la portion ($f/n$) de participants (ou de puissance informatique) problématique affecte la probabilité d'une défaillance de la sûreté du système (décision de deux propositions incompatibles), selon un choix de finalité.
% The maximum tolerated Byzantine presence $f$, is dependent on the choice of $\varepsilon$. Similar to Nakamoto consensus, given an observed Byzantine presence $f'$, where $f' \leq f$, the safety failure probability of our protocols maintains the property that $\varepsilon' \leq \varepsilon$. On the other hand, for classical consensus protocols, the failure probability is simply zero for all $f' \leq f$, and almost sure (i.e. one) for $f' > f$.

\begin{figure}[h]
    \includegraphics[width=\linewidth]{figures/safety-f-eps.pdf}
%O    \caption{Classical BFT protocols that tolerate $f$ failures will encounter total safety failure when the threshold is exceeded even by one additional node. The Bitcoin curve shows a typical finality choice for Bitcoin where a block is considered final when it is ``buried'' in a branch having 6 additional blocks compared to any other competing forks. Snowflake belongs to the Snow family, and it is configured with $k=10$, $\beta=150$. Snowflake-7,8 uses $\alpha=7$ and $\alpha=8$ respectively (see Section~\ref{sec:protocol} for the definition of $k$, $\alpha$ and $\beta$.}
    \caption{Les protocoles BFT classiques qui tolèrent $f$ défaillances rencontrent une défaillance totale de leur sûreté quand le seuil est dépaasé même d'un seul nœud supplémentaire. La courbe de Bitcoin montre un choix de finalité typique pour Bitcoin où un bloc est considéré final quand il est \guillemotleft\,enterré\,\guillemotright~ dans une branche sous 6 blocs supplémentaires par rapport aux autres branches concurrentes. Snowflake appartient à la famille Snow et est configuré avec $k=10$, $\beta=150$. Snowflake-7,8 utilise $\alpha=7$ et $\alpha=8$ respectivement (voir en section~\ref{sec:protocol} pour la définition de $k$, $\alpha$ et $\beta$.}
    \label{fig:fandepsilon}
\end{figure}

\tronly{%
\begin{figure}[h]
    \includegraphics[width=\linewidth]{figures/safety-f-eps-log.pdf}
    \caption{Figure~\ref{fig:fandepsilon} Axe des y en log.}
    \label{fig:fandepsilonlog}
\end{figure}
}{}

%O \paragraph{Liveness} All our protocols provide a non-zero probability guarantee of termination within a bounded amount of time. 
\paragraph{Vitalité} Tous nos protocoles fournissent une garantie de probabilité supérieure à zéro de terminaison dans un laps de temps donné.
%O This bounded guarantee is similar to various protocols such as Ben-Or~\cite{ben1983another} and longest-chain protocols.
Cette garantie de limite est similaire à celle de divers protocoles comme Ben-Or~\cite{ben1983another} et les protocoles de chaîne la plus longue.
%O In particular, for Nakamoto consensus, the number of required blocks for a transaction increases exponentially with the number of adversarial nodes, with an asymptote at $f = n/2$ wherein the number is infinite.
En particulier, pour le consensus Nakamoto, le nombre de blocs requis pour une transaction augmente exponentiellement avec le nombre de nœuds malveillants, avec une asymptote à $f = n/2$ où le nombre est infini. % wut?
%O In other words, the time required for finality approaches $\infty$ as $f$ approaches $n/2$\tronly{ (Figure~\ref{fig:livenessproperties}).}{.}
En d'autres termes, le temps nécessaire à la finalité approche $\infty$ quand $f$ approche $n/2$\tronly{ (Figure~\ref{fig:livenessproperties}).}{.}
%O Furthermore, the required number of rounds is calculable ahead of time, as to allow the system designer to tune liveness at the expense of safety. Lastly, unlike traditional consensus protocols and similar to Nakamoto, our protocols benefit from lower adversarial presence, as discussed in property P3 below.
De plus, le nombre requis de tours est calculable à l'avance, ce qui permet au concepteur du système de réglere la vitalité aux dépens de la sûreté. Enfin, contrairement aux protocoles de consensus traditionnels et semblablement à Nakamoto, nos protocoles bénéficient d'une moindre présence antagoniste, comme le détaille la propriété P3 ci-dessous.

\tronly{%
\begin{figure}[h!]
    \includegraphics[width=\linewidth]{figures/liveness-f-time.pdf}
%O    \caption{The relation between $f/n$ and the convergence speed, given $\varepsilon = 10^{-20}$. The left figure shows the expected number of blocks to guarantee $\varepsilon$ in Bitcoin, which, counter to commonly accepted folk wisdom, is not a constant $6$, but depends on adversary size to withhold the same $\varepsilon$. The right figure shows the maximum number of rounds required by Snowflake, where being different from Bitcoin, the asymptote is below $0.5$ and varies by the choice of parameters.}
    \caption{Relation entre $f/n$ et la vitesse de convergence pour $\varepsilon = 10^{-20}$. La figure de gauche montre le nombre attendu de blocs pour garantir $\varepsilon$ dans Bitcoin, qui, contrairement à la croyance populaire, n'est pas une constante $6$, mais dépend de la taille de l'adversaire pour maintenir le même $\varepsilon$. La figure de droite montre le nombre maximum de tours requis par Snowflake où, étant différent de Bitcoin, l'asymptote se trouve sous $0.5$ et varie selon les paramètres.}
    \label{fig:livenessproperties}
\end{figure}
}
